We are going to use the forecast package to make predictions  as we have time-series of electricity consumption
```{r}
require("lubridate")
require("data.table")
require("Metrics")
require("forecast")
require("tseries")
```


```{r}
data <- read.csv("/home/gkaiafas/datasets/Vimsen_csv/772926413094",sep = ",",col.names=c("Time", "kwh"), fill=FALSE, strip.white=TRUE)
```

We use data.table & lubricate to reveal years,months...
```{r}
data$kwh <- as.numeric(as.character(data$kwh))
data$Time <- ymd_hms(as.character(data$Time))
data <- data.table(data)
data <- data[, c("hour", "weekday", "quarter", "month", "year"):= list(hour(Time), wday(Time), quarter(Time), month(Time), year(Time))]
```

We have to see if we extremely high,negative ot zero values and handke them sensibly

```{r}
summary(data$kwh)
dim(data[kwh==0.000])
dim(data[kwh<0.000])
```

```{r}
data[kwh<=0.00]$kwh <- data[kwh<=0.00]$kwh*(-1)
data[kwh==0.00]$kwh <- min(data[kwh!=0.000]$kwh)
dim(data[kwh==0.000])
dim(data[kwh<0.000])
```

We want predict the last-Next hour_quarter of all hours in a day. We come up with an efficient slice of the given dataset.
The slice follows 3 levels and from high to low we have that:
1st level: Slice tha dataset based on the year quarter because We assume that focusing on year's quarters will give us an advantage 
to deal with similar tempratures so as electricity consumption
2nd level: Slice the dataset on each year's quarter based on weekdays. We assume that each weekday on each year's quarter might have similar 
load consumption
3rd level: Slice the dataset based on each hour. 
Finally we have u super slice of the dataset based on Year's quarter, Weekdays and Hours.
The following list will give us data.tables where each one of them will be a specific hour & weekday & year_quarter

```{r}
hour_weekday_quarterList <- list()
c <- 1
for (i in 1:4){
  for (j in 1:7){
  	for (ii in 0:23){
                 hour_weekday_quarterList[[c]] <- list(data[quarter==i][weekday==j][hour==ii])
				c = c+1
		}
	}
}
```

Print for example the 1st hour for weekday 2

```{r}
hour_weekday_quarterList[[26]][[1]]
```

We want to calculate the Mean Absolute Error of prediction using the auto.arima function in forecast package
The predictions are calculated in the following way:
We give as a time-serie all the data.table of each quarter except the last value. Then we take the Absolute Error of this prediction.
We repeat the process 4 times but in each process we go 1 measurement behind. So in the last-4th repeatation we feed the auto.arima 
with the data.table until the 4th element from the end and we want to predict the #rd element from the end.
```{r}
forecasting <- function(i){
        h2w1q1 <- hour_weekday_quarterList[[i]][[1]]
        train <- h2w1q1[1:(dim(h2w1q1)[1]-4)]$kwh
        fit <- auto.arima(train,seasonal=FALSE)
        predicted <- unlist(forecast(fit,h=1)[4])
        err1 <- ae(predicted,h2w1q1[(dim(h2w1q1)[1]-3)]$kwh)
        train <- h2w1q1[1:(dim(h2w1q1)[1]-3)]$kwh
        fit <- auto.arima(train,seasonal=FALSE)
        predicted <- unlist(forecast(fit,h=1)[4])
        err2 <- ae(predicted,h2w1q1[(dim(h2w1q1)[1]-2)]$kwh)
        train <- h2w1q1[1:(dim(h2w1q1)[1]-2)]$kwh
        fit <- auto.arima(train,seasonal=FALSE)
        predicted <- unlist(forecast(fit,h=1)[4])
        err3 <- ae(predicted,h2w1q1[(dim(h2w1q1)[1]-1)]$kwh)
        train <- h2w1q1[1:(dim(h2w1q1)[1]-1)]$kwh
        fit <- auto.arima(train,seasonal=FALSE)
        predicted <- unlist(forecast(fit,h=1)[4])
        err4 <- ae(predicted,h2w1q1[(dim(h2w1q1)[1])]$kwh)
    return(mean(err1,err2,err3,err4))
}
```

Rerepat forecasting function for each day. Elements in list are the mean error predicting repeatetively the 4 last values of the timeseries 
for all the hours during the day. So we get back the MAE of these predictions.
The previous list contains 672 elements so we want to divide it to 24hours in order to implement the forecasting function, we wrote before, on every hour.
The folllowing list will have the test error(mae) for a whole day sliced as we told before.
```{r eval=FALSE}
r1 <- seq(1, 672, 24)
r2 <- seq(24, 672, 24)
error_list_all_hours_weekday = list()
for (j in 1:28){
    for (i in r1[j]:r2[j]){
        new_list[[i]] <- forecasting(i)
    }
    error_list_all_hours_weekday[[j]] <- mean(unlist(new_list))
}
```

We write a new function predicting only the last quarter of the time-serie and implement it to sliced dataset
```{r}
forecasting_last_quarter <- function(i){
        h2w1q1 <- hour_weekday_quarterList[[i]][[1]]
        train <- h2w1q1[1:(dim(h2w1q1)[1]-1)]$kwh
        fit <- auto.arima(train,seasonal=FALSE)
        predicted <- unlist(forecast(fit,h=1)[4])
        err1 <- ae(predicted,h2w1q1[(dim(h2w1q1)[1])]$kwh)
    return(err1)
}
```

```{r eval=FALSE}
ARIMA_error_list_all_hours_weekday <- list()
for (i in 1:length(hour_weekday_quarterList)){
  ARIMA_error_list_all_hours_weekday[[i]] <- forecasting_last_quarter(i)
	}
```

We predict again the last hour-quarter using state-space model

```{r eval=FALSE}
ETS_error_list_all_hours_weekday <- list()
for (i in 1:length(hour_weekday_quarterList)){
  oo <- hour_weekday_quarterList[[i]][[1]]$kwh
	point <- oo[length(oo)]
	vec <- oo[1:length(oo)-1]
	frcst <- forecast(ets(vec,model="ZZZ"),h=1)[[2]][[1]]
	ETS_error_list_all_hours_weekday[[i]] <- ae(point, frcst)
	}
```

In order to decide if arima is better than state-space-models we compare the above resulted lists and pick the method with the lower error.

```{r eval=FALSE}
SelectETSInsteadOfARIMA <- unlist(EtsGreaterArima[!unlist(lapply(EtsGreaterArima, is.null))])
Lower_Error <- list()
for (i in 1:672){
  if (i %in% SelectETSInsteadOfARIMA){
		Lower_Error[[i]] <- forecasting_last_quarter(i)
	} else{
		Lower_Error[[i]] <- ets[i]
		}
}	
errors <- cbind(bb,unlist(Lower_Error))
```

We produce some descripteive statistics using the very easy R_function quantile
```{r}
setnames(errors, "V2", "ets&arima")  
quantile(errors$ets, c(.25, .4, .5, .75, .9, .95))
quantile(errors$arima, c(.25, .4, .5, .75, .9, .95))
quantile(unlist(Lower_Error), c(.25, .4, .5, .75, .9, .95))
```

Using the Lower_Error list we implement it, to predict whole days and get back the mean error for all hours, to have an aggregated view
of our predictions.
```{r}
r1 = seq(1, 672, 24)
r2 = seq(24, 672, 24)
error_list_all_hours_weekday = list()
new_list = list()
for (j in 1:28){ ## length of r1&r2=28
    for (i in r1[j]:r2[j]){
        new_list[[i]] = Lower_Error[i]
    }
    error_list_all_hours_weekday[[j]] = mean(unlist(new_list))
}
error_list_all_hours_weekday = unlist(error_list_all_hours_weekday)*100
print (error_list_all_hours_weekday)
print (quantile(error_list_all_hours_weekday, c(.25, .4, .5, .75, .9, .95)))
```

PLOT PREDICTED VS TRUE VALUES--- Weekdays in the 1st Quarter 
WE CHECK IF ARIMA IS BEETER THAN ETS AND FIT THE APPROPRIATE MODEL
Example 1st weekday
```{r}
kkkk = list()
for (i in r1[1]:r2[1]){
  if (i %in% SelectETSInsteadOfARIMA)
	{
		h2w1q1 = hour_weekday_quarterList[[i]][[1]]
        train = h2w1q1[1:(dim(h2w1q1)[1]-1)]$kwh
        fit <- auto.arima(train,seasonal=FALSE)
        predicted = unlist(forecast(fit,h=1)[4])
		kkkk[[i]] = predicted
	}else{
		oo = hour_weekday_quarterList[[i]][[1]]$kwh
    	point = oo[length(oo)]
    	vec = oo[1:length(oo)-1]
    	frcst = forecast(ets(vec,model="ZZZ"),h=1)[[2]][[1]]
		kkkk[[i]] = frcst	
}
	}
true_value = unlist(kkkk)
predicted = rep(r1[1],r2[1])
for (i in r1[1]:r2[1]){
    predicted[i-(r1[1]-1)] = tail(hour_weekday_quarterList[[i]][[1]]$kwh,n=1)
}
plot.ts(true_value,main="Blue--> predicted, Black-->True")
lines(predicted,col="blue")
```
